Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2017-12-19 eurocg/paper.tex
section changes, added commands for todonotes
title change

% Author metadata::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Maximal Symmetric Partial Edge Drawings With Degree $ > 2$}
%optional, in case that the title is too long; 
%the running title should fit into the top page column
\titlerunning{MaxSPEDs with degree $ > 2$}

@@

\newcommand{\martin}[1]{\todo[inline,color=blue!40]{MN: #1}}
\newcommand{\fabian}[1]{\todo[inline,color=pink!40]{FK: #1}}

@@

\section{Trees}
\fabian{Algorithm running in $O(k^2n)$ where $ k $ is the max degree of the tree.}

\section{Bridge? Cactus Graphs}
\fabian{Algorithm running in $ O(kn^2) $?}

\section{Series Parallel Graphs?}

>>>>

% Author metadata::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs}
%{Maximal Symmetric Partial Edge Drawings With Degree $ > 2$}
%optional, in case that the title is too long; 
%the running title should fit into the top page column
\titlerunning{MaxSPEDs with degree $ > 2$}

@@

\newcommand{\martin}[1]{\todo[inline,color=blue!40]{MN: #1}}
\newcommand{\fabian}[1]{\todo[inline,color=pink!40]{FK: #1}}
\newcommand{\birgit}[1]{\todo[inline,color=red!40]{BS: #1}}
\newcommand{\michael}[1]{\todo[inline,color=green!40]{MH: #1}}
\newcommand{\soeren}[1]{\todo[inline,color=orange!40]{SN: #1}}

@@

\section{Two Polynomial Cases}
\subsection{Trees}
\fabian{Algorithm running in $O(kn)$ where $ k $ is the max degree of the tree.}

\subsection{Cacti of Degree Three}
\fabian{Algorithm running in $ O(kn) $.}

\section{Conclusion}
